MixEth: efficient, trustless coin mixing service for Ethereum

### 2018-12-20 article/shortpaper/main.tex
Fixing short paper

\begin{algorithm}
	\caption{Off-chain public key shuffling algorithm for the $i$th shuffling round}\label{shufflingoffchain}
	\begin{algorithmic}[1]
		\State $PK_{i} \gets []
		,c\stackrel{\$}{\leftarrow}\mathbb{Z}_n,\pi\stackrel{\$}{\leftarrow}S_{|PK_{i-1}|}$
		\State $C^{*}_{i-1}\leftarrow read\ from\ MixEth\ contract$
		\State $PK_{i-1}\leftarrow read\ from\ MixEth\ contract\ the\ current\ sequence\ of\ shuffled\ public\ keys$
		\For{$j=0;j<|PK_{i-1}|;j++$}
		\State $PK_{i}[\pi(j)]=c*PK_{i-1}[j]$ 
		\EndFor
		\State $C^{*}_{i}=cC^{*}_{i-1}$

@@

\begin{algorithm}
	\caption{On-chain verification algorithm of incoming shuffle challenges}\label{verifyingshufflingoffchain}
	\hspace*{\algorithmicindent} \textbf{Input}$(PK_{i}, PK_{i-1}, proof_{DDH}(C^{*}_{i-1},s_{B}C^{*}_{i-1},C^{*}_{i},s_{B}C^{*}_{i})$ \\
	\begin{algorithmic}[1]
		\State $b\leftarrow verifyChaumPedersen(proof_{DDH}(C^{*}_{i-1},s_{B}C^{*}_{i-1}, C^{*}_{i},s_{B}C^{*}_{i})$ 
		\State $b^*\leftarrow0$
		\If {$b \land s_{B}C^{*}_{i-1}\in PK_{i-1}\land s_{B}C^{*}_{i} \notin PK_{i}$}
		\State $b^*\gets 1$
		\Else
		\State $b^*\gets 0$
		\EndIf
		\hspace*{\algorithmicindent} \textbf{Output:} $b^{*}$ 
	\end{algorithmic}   
\end{algorithm}

@@

On-chain storage is extremely expensive: it requires $\num[group-separator={,}]{20000}$ gas to store a $256$-bit number, however if a particular storage slot is already taken and one wants to overwrite it with a non-zero element than storing only consumes $\num[group-separator={,}]{5000}$ gas. To minimize on-chain storage costs, only the last two list of shuffled public keys are stored in the MixEth contract's permanent storage. Note that storing only the latest list of shuffled public keys would not be enough, since honest receivers could not prove to the contract that their shuffled public key is compromised unless also the last but first list of shuffled keys is also available for the contract to check the Chaum-Pedersen proof against. Such a storage structure implies that after uploading the new list of shuffled public keys, a challenging period should proceed in order to let receivers check the correctness of the shuffle and whether their shuffled public key is stored in the smart contract, see Figure \ref{fig:shuffleandchallenge}. Furthermore we also allow senders to shuffle and deposit new public keys at the same time, meaning that only $3$ on-chain transactions (shuffle, withdraw mixed coins and withdraw shuffling deposit) are sufficient to complete the protocol. We left it as a future work to determine the optimal ratio of mixed coins and shuffling deposits in order to incentivise correct shuffling.

A great advantage of the fully on-chain version of MixEth is that it allows dynamic anonymity sets. One could potentially deposit funds to the contract and shuffle public keys and leave funds in the mixing contract for indefinite amount of time. As soon as the anonymity set is large enough a receiver could withdraw their assets. The whole process is represented as a finite automata as shown in Figure \ref{fig:shuffleandchallenge}. A receiver in a MixEth contract with $N$ senders could withdraw their funds after $N^{'}$ shuffling rounds, where $N^{'}$ is arbitrary.  This dynamic nature of the contract could even lead to a single monolithic MixEth contract instead of having multiple MixEth contracts with significantly fragmented anonymity sets. A single MixEth contract is able to support the mixing of ether and ERC-20 compatible tokens as well. However note that the gas complexity of shuffling transactions grow linearly in the number of participants, therefore the fully on-chain implementation is not capable to support extremely large anonymity sets with participants more than cca. $\num[group-separator={,}]{800}$.

@@

Given these adaptations the application proceeds as follows, all participants including senders, shufflers and receivers, deposit funds in a mutli-signature wallet compatible with the Counterfactual framework, they then follow the installation protocols specified by the framework to install the adapted MixEth logic. Afterwards each participant signs a transaction that transfers an equal amount to each withdrawer from the multi-sig, dependent on correct execution of the channelised MixEth application logic. This application logic proceeds as follows: each sender names a public key of a shuffler as in the deposit stage of the on-chain application, then each shuffler takes it in turn to shuffle. After all shuffles have taken place each withdrawer is given a turn to either declare fraud or no-fraud on any shuffle round. Finally each withdrawer then provides proof of ownership by submitting a valid signature on the modified ECDSA scheme. If any of these steps does not occur, or does not occur correctly, the protocol aborts and the conditional transfer does not occur. In this case the perpetrator loses a deposit, either through fraud proof or through failure to take their turn when state is published on-chain. A further modification would be to distribute the slashed deposit to each of the other participants, compensating them for their lost time and the gas costs associated with proving the fault of the other party. Following this protocol the on-chain transactions are now reduced to: one transaction from each participant to deposit funds into the multi-sig, and a set of transactions that send funds from the multi-sig to each of the withdrawers and deposits back to each of the other participants. The modified procedure of the MixEth protocol is illustrated as a finite automate in Figure \ref{fig:shufflethenchallenge}. Note that all three $N$s are the same. In a channelised MixEth contract there are exactly $N$ depositors, $N$ shufflers and $N$ receivers.

\begin{table}[H] 
	\caption{Proof-of-concept implementation gas cost results. Expect further improvements. MixEthChannel refers to the implementation which leverages state channels for shuffling and challenging periods}
	\centering 
	\begin{tabular}{@{\extracolsep{6pt}}lccccc@{}} 	
		\toprule
		\hline
		&Deployment&Deposit&\multicolumn{2}{c}{Shuffle}& Withdraw\\
		\cline{4-5}&&&Shuffle upload&Challenge\\
		\hline
		\midrule
		Möbius \cite{meiklejohn2018mobius}     &$\num[group-separator={,}]{1046027}$&$\num[group-separator={,}]{76123}$&0&0&$\num[group-separator={,}]{335714}$n   \\
		Miximus \cite{miximus2018}&$\num[group-separator={,}]{1751378}$&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
		MixEth&TBD&$\num[group-separator={,}]{99254}$&$\num[group-separator={,}]{138653}+\num[group-separator={,}]{10000}n$&$\num[group-separator={,}]{227563}$&$\num[group-separator={,}]{113265}$  \\
		MixEthChannel&TBD&TBD&0&0&TBD\\
		\bottomrule
	\end{tabular}
	\label{table:gasproperties}
\end{table}

\bibliographystyle{plain}
\bibliography{sample}

>>>>

\begin{algorithm}[H]
	\caption{Off-chain public key shuffling algorithm for the $i$th shuffling round}\label{shufflingoffchain}
	\begin{algorithmic}[H]
		\State $PK_{i} \gets []
		,c\stackrel{\$}{\leftarrow}\mathbb{Z}_n,\pi\stackrel{\$}{\leftarrow}S_{|PK_{i-1}|}$
		\State $C^{*}_{i-1}\leftarrow read\ from\ MixEth\ contract$
		\State $PK_{i-1}\leftarrow read\ from\ MixEth\ contract\ the\ current\ sequence\ of\ shuffled\ public\ keys$
		\For{$j=0;j<|PK_{i-1}|;j++$}
		\State $PK_{i}[\pi(j)]=c*PK_{i-1}[j]$ 
		\EndFor
		\State $C^{*}_{i}=cC^{*}_{i-1}$

@@

\begin{algorithm}
	\caption{On-chain verification algorithm of incoming shuffle challenges}\label{verifyingshufflingoffchain}
	\hspace*{\algorithmicindent} \textbf{Input}$(PK_{i}, PK_{i-1}, proof_{ChP}(C^{*}_{i-1},s_{B}C^{*}_{i-1},C^{*}_{i},s_{B}C^{*}_{i})$ \\
	\begin{algorithmic}[1]
		\State $b\leftarrow verifyChaumPedersen(proof_{ChP}(C^{*}_{i-1},s_{B}C^{*}_{i-1}, C^{*}_{i},s_{B}C^{*}_{i})$ 
		\State $b^*\leftarrow0$
		\If {$b \land s_{B}C^{*}_{i-1}\in PK_{i-1}\land s_{B}C^{*}_{i} \notin PK_{i}$}
		\State $b^*\gets 1$
		\Else
		\State $b^*\gets 0$
		\EndIf
		\hspace*{\algorithmicindent} \textbf{Output:} $b^{*}$ 
	\end{algorithmic}   
\end{algorithm}

@@

On-chain storage is extremely expensive: it requires $\num[group-separator={,}]{20000}$ gas to store a $256$-bit number, however if a particular storage slot is already taken and one wants to overwrite it with a non-zero element than storing only consumes $\num[group-separator={,}]{5000}$ gas. To minimize on-chain storage costs, only the last two list of shuffled public keys are stored in the MixEth contract's permanent storage. Note that storing only the latest list of shuffled public keys would not be enough, since honest receivers could not prove to the contract that their shuffled public key is compromised unless also the last but first list of shuffled keys is also available for the contract to check the Chaum-Pedersen proof against. Such a storage structure implies that after uploading the new list of shuffled public keys, a challenging period should proceed in order to let receivers check the correctness of the shuffle and whether their shuffled public key is stored in the smart contract. Furthermore we also allow senders to shuffle and deposit new public keys at the same time, meaning that only $3$ on-chain transactions (shuffle, withdraw mixed coins and withdraw shuffling deposit) are sufficient to complete the protocol. We left it as a future work to determine the optimal ratio of mixed coins and shuffling deposits in order to incentivise correct shuffling.

A great advantage of the fully on-chain version of MixEth is that it allows dynamic anonymity sets. One could potentially deposit funds to the contract and shuffle public keys and leave funds in the mixing contract for indefinite amount of time. As soon as the anonymity set is large enough a receiver could withdraw their assets. A receiver in a MixEth contract with $N$ senders could withdraw their funds after $N^{'}$ shuffling rounds, where $N^{'}$ is arbitrary.  This dynamic nature of the contract could even lead to a single monolithic MixEth contract instead of having multiple MixEth contracts with significantly fragmented anonymity sets. A single MixEth contract is able to support the mixing of ether and ERC-20 compatible tokens as well. However note that the gas complexity of shuffling transactions grow linearly in the number of participants, therefore the fully on-chain implementation is not capable to support extremely large anonymity sets with participants more than cca. $\num[group-separator={,}]{800}$.

@@

Given these adaptations the application proceeds as follows, all participants including senders, shufflers and receivers, deposit funds in a mutli-signature wallet compatible with the Counterfactual framework, they then follow the installation protocols specified by the framework to install the adapted MixEth logic. Afterwards each participant signs a transaction that transfers an equal amount to each withdrawer from the multi-sig, dependent on correct execution of the channelised MixEth application logic. This application logic proceeds as follows: each sender names a public key of a shuffler as in the deposit stage of the on-chain application, then each shuffler takes it in turn to shuffle. After all shuffles have taken place each withdrawer is given a turn to either declare fraud or no-fraud on any shuffle round. Finally each withdrawer then provides proof of ownership by submitting a valid signature on the modified ECDSA scheme. If any of these steps does not occur, or does not occur correctly, the protocol aborts and the conditional transfer does not occur. In this case the perpetrator loses a deposit, either through fraud proof or through failure to take their turn when state is published on-chain. A further modification would be to distribute the slashed deposit to each of the other participants, compensating them for their lost time and the gas costs associated with proving the fault of the other party. Following this protocol the on-chain transactions are now reduced to: one transaction from each participant to deposit funds into the multi-sig, and a set of transactions that send funds from the multi-sig to each of the withdrawers and deposits back to each of the other participants.

\begin{table}[H] 
	\caption{Proof-of-concept implementation gas cost results. Expect further improvements. MixEthChannel refers to the implementation which leverages state channels for shuffling and challenging periods}
	\centering 
	\begin{tabular}{@{\extracolsep{6pt}}lccccc@{}} 	
		\toprule
		\hline
		&Deployment&Deposit&\multicolumn{2}{c}{Shuffle}& Withdraw\\
		\cline{4-5}&&&Shuffle upload&Challenge\\
		\hline
		\midrule
		Möbius \cite{meiklejohn2018mobius}     &$\num[group-separator={,}]{1046027}$&$\num[group-separator={,}]{76123}$&0&0&$\num[group-separator={,}]{335714}$n   \\
		Miximus \cite{miximus2018}&$\num[group-separator={,}]{1751378}$&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
		MixEth&TBD&$\num[group-separator={,}]{99254}$&$\num[group-separator={,}]{138653}+\num[group-separator={,}]{10000}n$&$\num[group-separator={,}]{227563}$&$\num[group-separator={,}]{113265}$  \\
		MixEthChannel&TBD&TBD&0&0&TBD\\
		\bottomrule
	\end{tabular}
	\label{table:gasproperties}
\end{table} 
\newpage
\bibliographystyle{plain}
\bibliography{sample}
